RNeXML: Parsing and Serializing the Next Generation of Phyloinformatic Data in R

### 2014-06-17 manuscripts/manuscript.Rmd
remove extraneous citations

We can then leverage the rich suite of methods available from the R
phylogenetics community (including coercion into other representations,
such as `ouch` `r citep(citation("ouch"))` and `phylobase` `r citep(citation("phylobase"))` phylogeny
formats). For instance, here we use the standard plotting function from
the `ape` package to plot the resulting `ape::phylo` object returned by
`get_trees`.

>>>>

We can then leverage the rich suite of methods available from the R
phylogenetics community. For instance, here we use the standard plotting function from
the `ape` package to plot the resulting `ape::phylo` object returned by
`get_trees`.
